Calendar-based graphics for visualising people's daily schedules

### 2017-07-05 main.Rmd
added abstract

---
author:
  - name: Earo Wang
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{earo.wang@monash.edu}
  - name: Di Cook
    affiliation: Monash Univeristy
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{dicook@monash.edu}
  - name: Rob J Hyndman
    affiliation: Monash Univeristy
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{rob.hyndman@monash.edu}
title:
  formatted: "Calendar-based graphics for visualising people's daily schedules"
  plain: "Calendar-based graphics for visualising people's daily schedules"
abstract: >
  The abstract of the article.
keywords:
  # at least one keyword must be supplied
  formatted: [calendar-based visualisation, temporal-context data]
  plain:     [calendar-based visualisation, temporal-context data]
preamble: >
  \usepackage{amsmath}
output: 
  rticles::jss_article:
  citation_package: biblatex
bibliography: ["references.bib", "packages.bib"]
---

@@

This work was originally motivated by studying foot traffic in the city of Melbourne [@ped]. Since 2009, there have been 43 installed sensors counting pedestrians every hour across downtown Melbourne. The dataset can shed lights into understanding people's daily schedules, or assisting administration and business planning. (FIGURE ?: weekday at multiple sensors) Figure (?) lends itself to a number of issues that make exploratory data visualisation challenging in many temporal-context applications involving human behaviours:

1. Variations primarily result from multiple time scales including time of day, day of week, and day of year (such as public holiday and recurred events).
2. Since the data are often collected at daily frequency or a time scale more frequent than daily, they typically involve large number of observations spanning over a long time period.
3. Measurements of a single type are made at multiple locations at a given time point, which creates a need in comparing and contrasting between locations.

@@

The remainder of the paper is organised as follows. Section \ref{sec:algorithm} describes the \code{frame_calendar} function and its construction in detail. Section \ref{sec:examples} presents examples using a range of geometric objects. Section \ref{sec:discussion} discusses the advantages and disadvantages of the method.

>>>>

---
author:
  - name: Earo Wang
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{earo.wang@monash.edu}
  - name: Di Cook
    affiliation: Monash Univeristy
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{dicook@monash.edu}
  - name: Rob J Hyndman
    affiliation: Monash Univeristy
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{rob.hyndman@monash.edu}
title:
  formatted: "Calendar-based graphics for visualising people's daily schedules"
  plain: "Calendar-based graphics for visualising people's daily schedules"
abstract: >
  It is often challenging to visualise people's daily schedules as the data are of multiple seasons and of long length. One such example is Melbourne pedestrian sensor data which are collected at hourly interval and at a number of locations. Owing to human-related activities, the primary depiction of the data features multiple temopral scales such as time of day, day of week, day of year. We introduce the \code{frame\_calendar} function that provides a method for rearranging such kind of data in a calendar-based format and accomplishing visualisation with the grammar of graphics, and describe its construction in detail. We provide some examples to demonstrate its usage by applying to the pedetrian data.
keywords:
  # at least one keyword must be supplied
  formatted: [calendar-based visualisation, temporal-context data]
  plain:     [calendar-based visualisation, temporal-context data]
preamble: >
  \usepackage{amsmath}
output: 
  rticles::jss_article:
  citation_package: biblatex
bibliography: ["references.bib", "packages.bib"]
---

@@

This work was originally motivated by studying foot traffic in the city of Melbourne [@ped]. There have been 43 installed sensors counting pedestrians every hour across downtown Melbourne until recently. The dataset can shed lights into understanding people's daily schedules, or assisting administration and business planning. (FIGURE ?: weekday at multiple sensors) Figure (?) lends itself to a number of issues that make exploratory data visualisation challenging in many temporal-context applications involving human behaviours:

1. Variations primarily result from multiple time scales including time of day, day of week, and day of year (such as public holiday and recurred events).
2. Since the data are often collected at daily frequency or a time scale more frequent than daily, they typically involve a large number of observations spanning over a long time period.
3. Measurements of a single type are made at multiple locations at a given time point, which creates a need in comparing and contrasting between locations.

@@

The remainder of the paper is organised as follows. Section \ref{sec:algorithm} describes the \code{frame_calendar} function and the detailed construction. Section \ref{sec:examples} presents some examples of its usage. Section \ref{sec:discussion} discusses the advantages and disadvantages of the method.

### 2017-07-05 main.tex
added abstract

\Abstract{
The abstract of the article.
}

@@

This work was originally motivated by studying foot traffic in the city
of Melbourne \citep{ped}. Since 2009, there have been 43 installed
sensors counting pedestrians every hour across downtown Melbourne. The
dataset can shed lights into understanding people's daily schedules, or
assisting administration and business planning. (FIGURE ?: weekday at
multiple sensors) Figure (?) lends itself to a number of issues that
make exploratory data visualisation challenging in many temporal-context
applications involving human behaviours:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Variations primarily result from multiple time scales including time
  of day, day of week, and day of year (such as public holiday and
  recurred events).
\item
  Since the data are often collected at daily frequency or a time scale
  more frequent than daily, they typically involve large number of
  observations spanning over a long time period.
\item
  Measurements of a single type are made at multiple locations at a
  given time point, which creates a need in comparing and contrasting
  between locations.
\end{enumerate}

>>>>

\Abstract{
It is often challenging to visualise people's daily schedules as the
data are of multiple seasons and of long length. One such example is
Melbourne pedestrian sensor data which are collected at hourly interval
and at a number of locations. Owing to human-related activities, the
primary depiction of the data features multiple temopral scales such as
time of day, day of week, day of year. We introduce the
\code{frame\_calendar} function that provides a method for rearranging
such kind of data in a calendar-based format and accomplishing
visualisation with the grammar of graphics, and describe its
construction in detail. We provide some examples to demonstrate its
usage by applying to the pedetrian data.
}

@@

This work was originally motivated by studying foot traffic in the city
of Melbourne \citep{ped}. There have been 43 installed sensors counting
pedestrians every hour across downtown Melbourne until recently. The
dataset can shed lights into understanding people's daily schedules, or
assisting administration and business planning. (FIGURE ?: weekday at
multiple sensors) Figure (?) lends itself to a number of issues that
make exploratory data visualisation challenging in many temporal-context
applications involving human behaviours:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Variations primarily result from multiple time scales including time
  of day, day of week, and day of year (such as public holiday and
  recurred events).
\item
  Since the data are often collected at daily frequency or a time scale
  more frequent than daily, they typically involve a large number of
  observations spanning over a long time period.
\item
  Measurements of a single type are made at multiple locations at a
  given time point, which creates a need in comparing and contrasting
  between locations.
\end{enumerate}
